---
title: "EVS Dynamic Report"
author: "Sarah Gonyo"
date: "2023-05-03"
output: html_document
params:
  country: AL
  outcome: job_priority
  control: NA
  age_poly: 1
---

```{r, include = FALSE}
library(dplyr)
library(tidyverse)
library(texreg) #regression tables
library(stringr)

#Import data
data_country <- if (params$country == "Overall"){
  data_subset
} else{
  data_subset %>%
    filter(country == params$country)
}
```
# Overview

The purpose of this project is to create an interactive [shiny app](https://www.shinyapps.io/admin/#/application/9020621) to understand attitudes towards gender roles and immigration using data from the European Value Study (EVS) from 2017. The EVS is a large-scale, cross-national and longitudinal survey research on how Europeans think about family, work, religion, politics, and society.   Visit [European Value Study](https://search.gesis.org/research_data/ZA7500#variables|exploredata-ZA7500_Varv80|0|variable_order|asc|v80) for more information.

The two variables of interest are agreement with the following statements:

 * When a mother works for pay, the children suffer
 * When jobs are scarce, employers should give priority to [NATIONALITY] people over immigrants
 
Two tabs are shown in the app. The first tab shows graphs exploring the relationship between the selected outcome variable and three controls: age, education, and sex. The second tab shows the coefficients and residuals plot of a regression analysis between the selected outcome variable and selected control variables.

Four inputs are required to use this app. First, select a country from the drop-down menu below. Next, select between two outcome variables. Then, select sex and/or education as your control variables (age is included by default). Finally, select the number of age polynomials you would like to include in the regression (e.g., selecting 3 includes age, age^2, and age^3).
 
# Main Findings

Figure 1 shows the relationship between the selected variable of interest and age, education, and sex.
```{r, warning = FALSE, echo = FALSE}
#Figures
if (params$outcome == "child_suffer") {
  data_country %>%
    ggplot(aes(
      x = age,
      y = child_suffer,
      color = as.factor(education)
    )) +
    geom_line(stat = "summary", fun = "mean") +
    labs(color = "Education", x = "Age", y = "When a mother works for pay, the children suffer") +
    facet_wrap(~ male,
               ncol = 1,
               labeller = label_value) +
    ggtitle(paste0(params$country, " Results"))
  
} else{
  data_country %>%
    ggplot(aes(
      x = age,
      y = job_priority,
      color = as.factor(education)
    )) +
    geom_line(stat = "summary", fun = "mean") +
    labs(color = "Education", x = "Age", y = "Employment priority to nationals over immigrants") +
    facet_wrap(~ male,
               ncol = 1,
               labeller = label_value) +
    ggtitle(paste0(params$country, " Results"))
}
```



```{r, include = FALSE}
#Regression
model <-
  
  if (params$control == "NA") {
    lm(
      formula = str_c(params$outcome, " ~ " , "poly(age, ", params$age_poly, ")"),
      data = data_country
    )
  } else {
    lm(
      formula = str_c(params$outcome, " ~ " ,
                      str_c(c(params$control, "+"), collapse = " + "),
        
        "poly(age, ", 1,")"),
      data = data_country
    )
  }
```
The regression model below explains the effects of selected inputs on the selected variable of interest.
 
```{r, echo = FALSE, message=FALSE, results='asis'}
htmlreg(model, booktabs = TRUE, dcolumn = TRUE, caption = "Regression Results")
```

Finally, the figure below shows a scatterplot of the predicted versus the residuals from the regression. 
```{r, warning = FALSE, echo = FALSE}
#Residuals plot
ggplot(model, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0) +
  labs(x = "Residuals", y = "Predicted") +
  ggtitle(paste0(params$country, " Predicted vs Residuals Plot")
  )
```




